Fish & Benthic Community data: Antigua, Barbuda, & Bonaire - Aug. 2017

### 2020-12-06 r/Analysis.Rmd
extra figs for defense slides

>>>>

```{r}
# testing size distribution...
sum_id_sub <- sum_id %>%
  filter(length_cm >= 15 & length_cm <= 30 & species_code %in% c("qup", "stop") & phase == "i")

ggplot(data = sum_id_sub, aes(x = site, y = length_cm, group = site)) +
  geom_boxplot() +
  facet_grid(. ~ species)

ggplot(data = sum_id_sub, aes(x = length_cm, group = site, fill = site)) +
  geom_density(alpha = 0.1)

lm <- lm(data = sum_ssp_pca, pc1_all ~ length_mean)
summary(lm) # not significantly correlated with PC1
```

### 2020-12-06 r/Paper_analyses.Rmd
extra figs for defense slides

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,2)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))
plot(g)

ggsave(here("figs/behavior_panel.png"),g)
```

>>>>

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,2)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))
plot(g)
ggsave(here("figs/behavior_panel.png"),g)
```

```{r}
# indv plots for slides

library(ggpubr)

fr_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_median-fr_se, ymax=fr_median+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = expression(Feeding~rate~(bites~min^-1)), 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=12),
        )

fr_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_median-fr_se, ymax=fr_median+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = "",
       title = "S. viride") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title.x = element_blank(),
        )

ggarrange(fr_qup, fr_stop, 
          #abels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "right")

ggsave(here("figs", "fr.png"), height = 3, width = 6)

fi_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_median-for_bites_se, ymax=for_bites_median+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = expression(Grazing~intensity~(bites~foray^-1)), 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=12),
        )

fi_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_median-for_bites_se, ymax=for_bites_median+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = "",
       title = "S. viride") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title.x = element_blank(),
        )

ggarrange(fi_qup, fi_stop, 
          #abels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "right")

ggsave(here("figs", "fi.png"), height = 3, width = 6)
```

### 2020-12-06 r/Sites.Rmd
updating stats
extra figs for defense slides

>>>>

## Sample sizes per site
```{r}
n_fish_tran <- fish %>% 
  filter(biomass != 0) %>% 
  group_by(site) %>%
  summarize(n_tran = max(transect)) %>%
  ungroup()

mean_fish_tran <- n_fish_tran %>%
  summarize(mean = mean(n_tran),
            sd = sd(n_tran),
            se = sd/sqrt(n()))

n_benthic_tran <- bent_tran %>% 
  group_by(site) %>%
  summarize(n_tran = max(transect)) %>%
  ungroup()

n_rugosity_tran <- ab_rugosity %>% 
  group_by(site) %>%
  summarize(n_tran = max(transect)) %>%
  ungroup()
```
